---
title: "PACTA Terminology Update: ALD becomes ABCD"
description: |
  Explaining the decision to change terminology from Asset-Level Data to 
  Asset-Based Company Data.
author:
  - name: Jackson Hoffart
    url: https://github.com/jdhoffa
date: 2022-03-02
output: 
  distill::distill_article:
  toc: true
  toc_depth: 3
  self_contained: true
categories:
  - methodology
preview: preview.jpg
twitter:
  site: "@jdhoffart"
  creator: "@jdhoffart"
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

``` {r packages, echo=FALSE}
suppressPackageStartupMessages(library(dplyr))
library(r2dii.data)
library(gt)
```

The PACTA team has recently decided to update the terminology used to refer to a
crucial dataset. The dataset that was previously known as "Asset-Level Data"
(ALD) will henceforth be referred to as "Asset-Based Company Data" (ABCD). This 
note explains our reasoning. 

## Explanation

The PACTA methodology depends fundamentally on 3 input datasets:

- Portfolio data (portfolios, loanbooks, etc.)
- Climate change mitigation scenarios
- Data on the production of physical assets 

Historically, this last dataset was referred to as the "Asset-Level Data" (ALD). 
This name was a natural choice, since the underlying data describes the 
production of physical assets that are owned and operated by various companies 
globally.

One might imagine an asset-level dataset containing the following information:

``` {r, echo = FALSE}

ald <- tibble::tribble(
  ~asset_id,          ~asset_name, ~sector,     ~technology, ~year, ~production, ~production_unit, ~plant_location,
         1L,        "a wind farm", "power", "renewablescap", 2020L,        100L,             "MW",            "ES",
         1L,        "a wind farm", "power", "renewablescap", 2025L,        200L,             "MW",            "ES",
         2L, "a coal-fired plant", "power",       "coalcap", 2020L,        500L,             "MW",            "DE",
         2L, "a coal-fired plant", "power",       "coalcap", 2025L,        300L,             "MW",            "DE"
  )

ald %>% 
  gt() %>%
  tab_header(
    title = "Asset-Level Data"
  ) %>% 
  cols_label(
    asset_id = "Asset ID",
    asset_name = "Asset Name",
    sector = "Sector",
    technology = "Technology",
    year = "Year",
    production = "Capacity",
    production_unit = "Capacity Unit",
    plant_location = "Plant Location"
  )

```

In the table above, data is given out directly at the level of the physical 
asset.

However, what is actually used in PACTA has already been pre-processed. It looks
something like this:

``` {r, echo = FALSE}

ald_demo %>%
  head() %>%  
  select(
    company_id, 
    name_company, 
    sector, 
    technology, 
    year, 
    production, 
    production_unit, 
    plant_location, 
    country_of_domicile
    ) %>% 
  gt() %>%
  tab_header(
    title = "Asset-Based Company Data"
  ) %>% 
  cols_label(
    company_id = "Company ID",
    name_company = "Company Name",
    sector = "Sector",
    technology = "Technology",
    year = "Year",
    production = "Capacity",
    production_unit = "Capacity Unit",
    plant_location = "Plant Location",
    country_of_domicile = "Country of Domicile"
  )

```

Notice that, while the data itself is based on information at the physical
asset-level, it has already been connected to owning companies. In fact, the
production and/or capacity of each physical asset has been aggregated to every
company that owns a portion of it, all the way up the corporate tree. In this 
sense, the data is not really at the "Asset-Level" but rather the 
"Company-Level".

Though a subtle point, this discrepancy has caused some confusion, and given how
crucial the dataset is to the operation of PACTA, we have elected to give it a 
more clear name. Henceforth, we will now refer to this data as 
"Asset-Based Company Data" or ABCD.