---
title: "r2dii.analysis 0.1.0 is now on CRAN"
description: |
  This release includes a significant rework of the `target_sda` function, and 
  several bugfixes. 
author:
  - name: Mauro Lepore
    url: https://github.com/jdhoffa
base_url: https://2degreesinvesting.github.io/
date: 08-21-2020
output: 
  distill::distill_article:
    toc: true
    toc_depth: 3
    self_contained: true
categories:
  - r2dii
  - package
twitter:
  site: "@jdhoffart"
  creator: "@jdhoffart"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  collapse = TRUE,
  comment = "#>"
)
```

r2dii.analysis 0.1.0 is now on CRAN. r2dii.analysis provides analysis tools to help you study how financial assets align to climate scenarios.

This release signals that r2dii.analysis is now [maturing](https://www.tidyverse.org/lifecycle/#maturing). You can install it from CRAN with:

```r
install.packages("r2dii.analysis")
```

Then use it with:

```{r}
library(r2dii.analysis)
```

Let's also load the rest of the `r2dii` suite. I also use the package dplyr; it is not necessary but convenient.

```{r}
library(r2dii.data)
library(r2dii.match)
library(dplyr)
```

All user-facing changes are listed in the [changelog](https://2degreesinvesting.github.io/r2dii.analysis/news/index.html); here I'll show the most important ones.

We fixed a bug in the dataset `target_sda`; it now outputs targets calculated using the ald-adjusted scenarios. 

```{r}
match_result <- loanbook_demo %>% 
  match_name(ald_demo) %>% 
  prioritize()

match_result %>% 
  target_sda(
    ald_demo,
    co2_intensity_scenario_demo
    )
```

We have also added the parameter `weight_production` to `target_market_share`. This allows you to choose between outputting production values, weighted by relative loan size (`weight_production == TRUE`), or to output the actual raw company production values (`weight_production == FALSE`).

```{r}
match_result <- loanbook_demo %>% 
  match_name(ald_demo) %>% 
  prioritize()

match_result %>% 
  target_market_share(
    ald_demo,
    scenario_demo_2020,
    region_isos_demo,
    # using weighted production
    weight_production = TRUE
  ) %>% 
  filter(production_metric == "projected")

match_result %>% 
  target_market_share(
    ald_demo,
    scenario_demo_2020,
    region_isos_demo,
    # using weighted production
    weight_production = FALSE
  ) %>% 
  filter(production_metric == "projected") %>% 
  select(-c(tmsr, smsp))
```

## Acknowledgements

```{r echo=FALSE}
thank <- function(x) {
  x <- sort(x)
  paste0("[", x, "]", sprintf("(https://github.com/%s)", x), collapse = ", ")
}
contributors <- c(
  "jdhoffa",
  "maurolepore"
)
```

While this release includes commits from only a few of us (`r thank(contributors)`), it is thanks to ideas and feedback from many more colleagues at 2DII.

